---
title: "checkI_example"
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  messages = FALSE,
  warnings = FALSE
)
```
```

## R Markdown

This is an R package for visualization and supervised cell annotation of Vectra Polaris and MIBI data. The package provides basic marker visualization tools like: heat-map and ridge plot. Given a set of annotated training images, it can also perform a random forest based cell phenotyping for non-annotated images. 


```{r reading data}
require(VectraMIBI)
require(dplyr)
require(data.table)
require(pheatmap)
require(ggplot2)
require(ggridges)

n_cores = parallel::detectCores()-1
full_data = read.csv("Data/Full_cellData_pruned.csv")
train_data = read.csv("Data/Training_Data.csv")
```

```{r summary cell counts}
#-----Summary of cell proportions-------------------
summ_cell(full_data)

```


```{r heatmap}
#-----Generate Heatmaps of different kinds------------
df = train_data[,-c(1,2)]
#genheatmap(df,is.log=FALSE)
genheatmap(df,is.log=TRUE)