---
title: "VectraMIBI_example"
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  messages = FALSE,
  warnings = FALSE
)
```
```

## VectraMIBI

This is an R package for visualization and supervised cell annotation of Vectra Polaris and MIBI data. The package provides basic marker visualization tools like: heat-map and ridge plot. Given a set of annotated training images, it can also perform a random forest based cell phenotyping for non-annotated images. 


#
First we load the required packages and import the training dataset (named as "train_data") which has marker data for different cells from different images and all the cells are annotated. The first two columns of the training dataset respectively correspond to the image number and the cell number inside that image number. 

```{r reading data}
require(VectraMIBI)
require(dplyr)
require(data.table)
require(pheatmap)
require(ggplot2)
require(ggridges)

n_cores = parallel::detectCores()-1
full_data = read.csv("Data/Full_cellData_pruned.csv")
train_data = read.csv("Data/Training_Data.csv")
```

```{r summary cell counts}
#-----Summary of cell proportions-------------------
summ_cell(full_data)

```


```{r heatmap}
#-----Generate Heatmaps of different kinds------------
df = train_data[,-c(1,2)]
#genheatmap(df,is.log=FALSE)
genheatmap(df,is.log=TRUE)
```



```{r ridge plots}
#------Ridge-plot generator--------------

#interested_traits = c("Vimentin", "SMA", "CD45", "CD31", "Beta.catenin","Keratin6" )
interested_trait = c("Vimentin")
ridge_plottter(train_data,interested_trait,is.log="TRUE")
```




When you click the **Knit** button a document will be generated that includes both content as well as the output of any embedded R code chunks within the document. You can embed an R code chunk like this:

```{r cars}
summary(cars)
```

## Including Plots

You can also embed plots, for example:

```{r pressure, echo=FALSE}
plot(pressure)
```

Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.
